Allocate landings to Georges Bank EPU

### 2021-03-12 docs/allocateLandingsEPU.Rmd

```{r calc_props_sp, eval=T, out.width="100%",fig.align='center',fig.cap="Proportion of landings in GB relative to statistical area"}
source(here::here("data-raw","plot_landings_proportions.r"))
plot_landings_proportions(species="cols")

The same data is represented in the plot below but the species are plotted as rows instead of columns

```{r calc_props_st, eval=T, out.width="100%",fig.align='center',fig.cap="Proportion of landings in GB relative to statistical area"}
plot_landings_proportions(species="rows")

@@

```{r calc_lands,  eval=T, out.width="100%",fig.align='center',fig.cap="Total landings by statistical area"}
source(here::here("data-raw","plot_landings.r"))
plot_landings()

>>>>

```{r calc_props_st, eval=T, out.width="100%",fig.align='center',fig.height=10,,fig.cap="Proportion of landings in GB relative to statistical area"}
source(here::here("data-raw","plot_landings_proportions.r"))
plot_landings_proportions(species="rows")

@@

```{r calc_lands,  eval=T, out.width="100%",fig.align='center',fig.height=10,fig.cap="Total landings by statistical area"}
source(here::here("data-raw","plot_landings.r"))
plot_landings()
